Deriving Multi-Headed Projective Dependency Parses from Link Grammar Parses

### 2014-11-20 doc/LinksToDAG_final.tex
removed the last reference to the supplementary material url

The resulting English corpus uses a syntactic annotation scheme that is somewhat different from the CoNLL annotations.  Differences are tabulated in
Appendix~\ref{app:linktypes}, while the actual parses are contrasted in Appendix~\ref{app:parses}.  
By permission of the program chairs, these appendices are available at the anonymous URL \url{http://tidyurl.com/LinksToDAG_supplement}.  
Fragments are shown in Table~\ref{tab:linktypes} and Figure~\ref{fig:parses}.

>>>>

The resulting English corpus uses a syntactic annotation scheme that is somewhat different from the CoNLL annotations.  Differences are tabulated in
Appendix~\ref{app:linktypes}, while the actual parses are contrasted in Appendix~\ref{app:parses}, and fragments of these are shown in Table~\ref{tab:linktypes} and Figure~\ref{fig:parses}.
%By permission of the program chairs, these appendices are available at the anonymous URL \url{http://tidyurl.com/LinksToDAG_supplement}.
